---
title: "Assignment_5_Heinz_Konrad"
author: "K Heinz"
date: "1/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The link to my GitHub repository: https://github.com/didominasi/AssigmnmentV.git


## 3. Interacting with the API - the basics

The content of the response is spread on 3 different object: "_embedded", "links" and "page".
The first contains a list of 20 venues in Germany which store some information variables
about each venue. The "_links" object contains several links (href) to the first,
current, next last page containing 20 venues each. The page object gives us information
about the size of each page (20 venues), the number of pages/elements overall and
the current page:

The information is spread on 238 pages overall (page -> "totalPages" = 238").
total elements: content_viG[["page"]][["totalPages"]] --> 238
total elements:   content_viG[["page"]][["totalElements"]]  --> 4743

```{r first}

rm(list = ls())

if (!require("jsonlite")) install.packages("jsonlite")
if (!require("httr")) install.packages("httr")
if (!require("rlist")) install.packages("rlist")
if (!require("tidyverse")) install.packages("tidyverse")
if (!require("naniar")) install.packages("naniar")

library(jsonlite)
library(httr)
library(rlist)
library(tidyverse)
library(naniar)

source("/home/weide/api_key.R")

# This is the base_url that I will refer to
base_url <- "https://app.ticketmaster.com/discovery/v2/"

# I paste together the url to request the venues, after I access the API (Get) and read the response
get_url <- paste0(base_url, "venues.json?countryCode=DE&locale=*&apikey=", apikey)
venues_in_Germany <- GET(get_url)
content_viG <- content(venues_in_Germany)


# I create an empty data frame
n = content_viG[["page"]][["size"]]

df_germany1 <-
  data.frame(
    name = character(n),
    city = character(n),
    postalCode = character(n),
    address = character(n),
    url = character(n),
    longitude = numeric(n),
    latitude = numeric(n),
    stringsAsFactors = FALSE
  )

# I create a loop through all venues on the page. I extract the id for each venue and use it
# to access the variables within the response. I use several tests as explained in 4)

for (i in seq(1, n)){
  
  id <- (content_viG[["_embedded"]][["venues"]])[[i]][["id"]]
  combined_url <- paste0(base_url, "venues/", id, ".json?locale=*&apikey=", apikey )
  search_result <- GET(combined_url)
  cont_search_result <- content(search_result)
  
  if (("name" %in% names(cont_search_result)) == TRUE){
  df_germany1[i,1] <- cont_search_result$name
  }else{df_germany1[i,1] <- NaN}
  if (("city" %in% names(cont_search_result)) == TRUE){
  df_germany1[i,2] <- cont_search_result$city$name
  }else{ df_germany1[i,2] <- NaN}
  if (("postalCode" %in% names(cont_search_result)) == TRUE){
  df_germany1[i,3] <- cont_search_result$postalCode
  }else{df_germany1[i,3] <- NaN}
  if (("postalCode" %in% names(cont_search_result)) == TRUE){
  df_germany1[i,4] <- cont_search_result$address
  }else{df_germany1[i,4] <- NaN}
  if (("postalCode" %in% names(cont_search_result)) == TRUE){
  df_germany1[i,5] <- cont_search_result$url
  }else{df_germany1[i,5] <- NaN}
  if (("location" %in% names(cont_search_result) == TRUE) &&
        (as.numeric(cont_search_result$location$longitude) <= 15.043611) &&
        (as.numeric(cont_search_result$location$longitude) >= 5.866944) &&
        (as.numeric(cont_search_result$location$latitude) >= 47.271679) &&
        (as.numeric(cont_search_result$location$latitude) <= 55.0846)){
  df_germany1[i,6] <- cont_search_result$location$longitude
  df_germany1[i,7] <- cont_search_result$location$latitude
  }else { df_germany1[i,6] <- NaN
          df_germany1[i,7] <- NaN
  }
    Sys.sleep(0.25)


}


```

## 4. Interacting with the API - advanced

I use a for loop to access all the pages that contain venues in Germany.
After creating the empty dataframe I loop through the number of pages in the outer
for-loop. For each page, I create the url for the API request for the link for the 
consecutive page. After using "GET" and "content" I use another (inner) for loop
through all venues on each page to access this content. In each iteration of this 
loop one page (usually 20 venues) are filled in the previously created dataset.
For each variable I check if the requested variable of the venue is available.
Even though this is the case for the vast majority, there are some variables that 
have some missing values which causes the entire programm to hault.
For the location (long/lat) I implement another test in order to set all coordinates
that are not within the border of the nation-state to NaN.

```{r second, message= FALSE, warning= FALSE}

num <- as.numeric(content_viG[["page"]][["totalElements"]])

df_germany <-
  data.frame(
    name = character(num),
    city = character(num),
    postalCode = character(num),
    address = character(num),
    url = character(num),
    longitude = numeric(num),
    latitude = numeric(num),
    stringsAsFactors = FALSE
  )


total_number_pages <- content_viG[["page"]][["totalPages"]]

for (j in seq(0, total_number_pages - 1)){

# In this outer loop the pages are requested
next_page <- paste0(base_url, "venues.json?countryCode=DE&page=" , j , "&locale=*&apikey=", apikey)
next_page_url <- GET(next_page)
cont_next <- content(next_page_url)

number_venues <- length(cont_next[["_embedded"]][["venues"]])

  for (i in seq(1, number_venues)){
    
    # In this inner loop the details of each venue (venue ID) is requested.
    id <- (cont_next[["_embedded"]][["venues"]])[[i]][["id"]]
    combined_url <- paste0(base_url, "venues/", id, ".json?locale=*&apikey=", apikey )
    search_result <- GET(combined_url)
    cont_search_result <- content(search_result)
    
    if (("name" %in% names(cont_search_result)) == TRUE){
    df_germany[(j * 20 + i),1] <- cont_search_result$name
    }else{df_germany[(j * 20 + i),1] <- NaN
    }
    if (("city" %in% names(cont_search_result)) == TRUE){
    df_germany[(j * 20 + i),2] <- cont_search_result$city$name
    }else{ df_germany[(j * 20 + i),2] <-NaN
    }
    if (("postalCode" %in% names(cont_search_result)) == TRUE){
    df_germany[(j * 20 + i),3] <- cont_search_result$postalCode
    }else{ df_germany[(j * 20 + i),3] <-NaN
    }
    if (("address" %in% names(cont_search_result) == TRUE) &&
        (length(cont_search_result$address) != 0)) {
    df_germany[(j * 20 + i),4] <- cont_search_result$address
    }else { df_germany[(j * 20 + i),4] <- NaN
    }
    if (("url" %in% names(cont_search_result)) == TRUE){
    df_germany[(j * 20 + i),5] <- cont_search_result$url
    }else{df_germany[(j * 20 + i),5] <- NaN
    }
    # I check if the long/lat are located within the borders of Germany.
    if (("location" %in% names(cont_search_result) == TRUE) &&
        (as.numeric(cont_search_result$location$longitude) <= 15.043611) &&
        (as.numeric(cont_search_result$location$longitude) >= 5.866944) &&
        (as.numeric(cont_search_result$location$latitude) >= 47.271679) &&
        (as.numeric(cont_search_result$location$latitude) <= 55.0846)){
      df_germany[(j * 20 + i),6] <- cont_search_result$location$longitude
      df_germany[(j * 20 + i),7] <- cont_search_result$location$latitude
    }else{ df_germany[(j * 20 + i),6] <- NaN
           df_germany[(j * 20 + i),7] <- NaN
    }
  # The loop is supposed to halt as soon as the total number of Elements is reached.
  totalElements <- content_viG[["page"]][["totalElements"]]
  if ((j * 20 + i) == totalElements){break}
  Sys.sleep(0.2)
  }
} # outer for-loop
  
```

## 5. Visualizing the extracted data


I include the locations with geom_point and adopt the titles & lables. I convert
the longitude and latitude to a numeric values.



```{r third, message= FALSE, warning= FALSE}

library(ggplot2)

ggplot() +
  geom_polygon(
    aes(x = long, y = lat, group = group), data = map_data("world", region = "Germany"),
    fill = "grey90",color = "black") +
  theme_void() + coord_quickmap() +
  geom_point(data= df_germany, aes(x = as.numeric(longitude), y = as.numeric(latitude))) +
  labs(title = "Event locations across Germany", caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
    plot.caption = element_text(face = "italic")) +
    ylim(47.271679, 55.0846)
    #xlim(5.866944, 15.043611) 





```

## 6. Event locations in other countries

I chose to use Belgium (BE) as the second country.
In the following I merely adjusted the code of task 3,4 and 5 respectively for
Belgium.




```{r fourth, message= FALSE, warning= FALSE}

######## NR. 3   #########


get_url_be <- paste0(base_url, "venues.json?locale=*&countryCode=BE&apikey=", apikey)

venues_in_belgium <- GET(get_url_be)
content_viB <- content(venues_in_belgium)


m = 20

df_belgium1 <-
  data.frame(
    name = character(m),
    city = character(m),
    postalCode = character(m),
    address = character(m),
    url = character(m),
    longitude = numeric(m),
    latitude = numeric(m),
    stringsAsFactors = FALSE
  )




for (i in seq(1,20)){
  
  id_be <- (content_viB[["_embedded"]][["venues"]])[[i]][["id"]]
  combined_url_be <- paste0(base_url, "venues/", id_be, ".json?locale=*&apikey=", apikey )
  search_result_be <- GET(combined_url_be)
  cont_search_result_be <- content(search_result_be)
  
  if (("name" %in% names(cont_search_result_be)) == TRUE){
  df_belgium1[i,1] <- cont_search_result_be$name
  }else{df_belgium1[i,1] <- NaN}
  if (("city" %in% names(cont_search_result_be)) == TRUE){
  df_belgium1[i,2] <- cont_search_result_be$city$name
  }else{df_belgium1[i,2] <- NaN}
  if (("postalCode" %in% names(cont_search_result_be)) == TRUE){
  df_belgium1[i,3] <- cont_search_result_be$postalCode
  }else{df_belgium1[i,3] <- NaN}
  if (("address" %in% names(cont_search_result_be)) == TRUE){
  df_belgium1[i,4] <- cont_search_result_be$address
  }else{df_belgium1[i,4] <- NaN}
  if (("url" %in% names(cont_search_result_be)) == TRUE){
  df_belgium1[i,5] <- cont_search_result_be$url
  }else{df_belgium1[i,5] <- NaN}
  if (("location" %in% names(cont_search_result_be) == TRUE) &&
    (as.numeric(cont_search_result_be$location$longitude) <= 6.3831) &&
    (as.numeric(cont_search_result_be$location$longitude) >= 2.583333) &&
    (as.numeric(cont_search_result_be$location$latitude) >= 49.5072) &&
    (as.numeric(cont_search_result_be$location$latitude) <= 51.4978)){
  df_belgium1[i,6] <- cont_search_result_be$location$longitude
  df_belgium1[i,7] <- cont_search_result_be$location$latitude
  }else { df_belgium1[i,6] <- NaN
          df_belgium1[i,7] <- NaN
  }
    Sys.sleep(0.2)

}



######## NR. 4   #########


num_be <- as.numeric(content_viB[["page"]][["totalElements"]])

df_belgium <-
  data.frame(
    name = character(num_be),
    city = character(num_be),
    postalCode = character(num_be),
    address = character(num_be),
    url = character(num_be),
    longitude = numeric(num_be),
    latitude = numeric(num_be),
    stringsAsFactors = FALSE
  )


total_number_pages_be <- content_viB[["page"]][["totalPages"]]

for (j in seq(0, total_number_pages_be -1)){
next_page_be <- paste0(base_url, "venues.json?locale=*&countryCode=BE&page=" , j , "&apikey=", apikey)
next_page_url_be <- GET(next_page_be)
cont_next_be <- content(next_page_url_be)

number_venue_list <- length(cont_next_be[["_embedded"]][["venues"]])

  for (i in seq(1, number_venue_list)){
    
    id_be <- (cont_next_be[["_embedded"]][["venues"]])[[i]][["id"]]
    combined_url_be <- paste0(base_url, "venues/", id_be, ".json?locale=*&apikey=", apikey )
    search_result_be <- GET(combined_url_be)
    cont_search_result_be <- content(search_result_be)
    
    if (("name" %in% names(cont_search_result_be)) == TRUE){
    df_belgium[(j * 20 + i),1] <- cont_search_result_be$name
    }else{df_belgium[(j * 20 + i),1] <- NaN
    }
    if (("city" %in% names(cont_search_result_be)) == TRUE){
    df_belgium[(j * 20 + i),2] <- cont_search_result_be$city$name
    }else {df_belgium[(j * 20 + i),2] <- NaN
    }
    if (("postalCode" %in% names(cont_search_result_be)) == TRUE){
    df_belgium[(j * 20 + i),3] <- cont_search_result_be$postalCode
    }else{ df_belgium[(j * 20 + i),3] <- NaN
    }
    if (("address" %in% names(cont_search_result_be)) == TRUE){
    df_belgium[(j * 20 + i),4] <- cont_search_result_be$address
    }else { df_belgium[(j * 20 + i),4] <- NaN
    }
    if (("url" %in% names(cont_search_result_be)) == TRUE){
    df_belgium[(j * 20 + i),5] <- cont_search_result_be$url
    } else{  df_belgium[(j * 20 + i),5] <- NaN
    }
    if (("location" %in% names(cont_search_result_be) == TRUE) &&
    (as.numeric(cont_search_result_be$location$longitude) <= 6.3831) &&
    (as.numeric(cont_search_result_be$location$longitude) >= 2.583333) &&
    (as.numeric(cont_search_result_be$location$latitude) >= 49.5072) &&
    (as.numeric(cont_search_result_be$location$latitude) <= 51.4978)){
    df_belgium[(j * 20 + i),6] <- cont_search_result_be$location$longitude
    df_belgium[(j * 20 + i),7] <- cont_search_result_be$location$latitude
    }else { df_belgium[(j * 20 + i),6] <- NaN
            df_belgium[(j * 20 + i),7] <- NaN
    }
  totalElement_be <- content_viB[["page"]][["totalElements"]]
  if ((j*20 + 1) == totalElement_be){break}
  Sys.sleep(0.2)
  }

} # outer for-loop


######## NR. 5   #########



  venues_be <- df_belgium[, 6:7]

  ggplot() +
    geom_polygon(
      aes(x = long, y = lat, group = group), data = map_data("world", region = "Belgium"),
      fill = "grey90",color = "black") +
    theme_void() + coord_quickmap() +
    geom_point(data= venues_be, aes(x = as.numeric(longitude), y = as.numeric(latitude))) +
    labs(title = "Event locations across Belgium", caption = "Source: ticketmaster.com") +
    theme(title = element_text(size=8, face='bold'),
      plot.caption = element_text(face = "italic")) +
      ylim(49.5072, 51.4978) 
      #xlim(6.3831, 2.583333) 

 



  

```